We Are All Trying to Describe Something And We Don't Have the Words

### 2023-04-17 outputs/paper/paper.qmd
visceral

## Jack-iness and What Danceability Tells Us {#sec-first-point}

@@

library(tidyverse)

@@

@@

df |>
  arrange(desc(danceability)) |>
  select(artist_name, danceability, track_name)

## Third discussion point

It only makes sense, of course, to hire a bunch of undergrads and get them to tell us whether or not a few thousand songs are danceable, and then build our own danceability metric, and see if we get the same results -- that danceability is the characteristic that helps us best understand what makes Jack, Jack.

A major weakness is cooked into the dataset. Since we're not in the studio, we can't know the degree of Jack-iness in each individual song. Especially when he takes on the role of a more backseat co-producer, as he did with Lana Del Rey's Did You Know There's a Tunnel Under Ocean Blvd? \[tk\].

>>>>

## Danceability Predicts Jack-iness {#sec-first-point}

@@

@@

## But Danceability isn't even about Dancing! I propose: Visceral-ness

I am thinking about what Gamman said in his video.

> I did use the phrase "visceral hatred". But i did so only to describe my visceral hatred. I can't stand the sound of it. I hate it. And the way in which I hate it is viscerally. But I didn't go beyond that because it doesn't go beyond that. Nothing against the guy, I like Taylor swift's stuff. It's just subjective taste.

It's just his subjective taste, but in one way Gamman was actually totally on the money about this. The danceability variable, which is the strongest predictor of Jack-ness, seems to actually be more about "visceral"-ness when you do a close-listen of the songs with the highest danceability scores. The reason Jack is getting under people's skin could just be because his music... gets underneath your skin. Right to the viscera.

One fundamental weakness is cooked into the dataset. Since we're not in the studio, we can't know the degree of Jack-iness in each individual song. Especially when he takes on the role of a more backseat co-producer, as he did with Lana Del Rey's Did You Know There's a Tunnel Under Ocean Blvd? \[tk\].

#### Could our model just be predicting Jack via Taylor Swift?

```{r}
#| echo: false
#| warning: false
df %>%
  filter(jack == 1) %>%
  ggplot(aes(x = artist_name, y = danceability)) +
  geom_boxplot() +
  ggtitle("Boxplot of Danceability by Artist") +
  coord_flip()
```

@@

#### Next Steps

It only makes sense, of course, to hire a bunch of undergrads and get them to tell us whether or not a few thousand songs are visceral, and then build our own visceral-ness metric, and see if we get the same results -- that danceability is just visceral-ness in a trench coat, and that visceral-ness is the characteristic that helps us best understand what makes Jack, Jack.
